COG-ED Manuscript

### 2021-10-21 06_Paper/COG-ED/Manuscript.Rmd
created demo data for AUC

require(gtools)
demo_data = data.frame(level = rep(1:4,24))
sv = permutations(n = 4, r = 4, v = c(0.1,0.4,0.85,1))
m = 1
for (n in 1:nrow(demo_data)) {
  demo_data$subject[m:(m+3)] = rep(n,4)
  demo_data$sv[m:(m+3)] = sv[n,]
  m = m + 4
}
subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
demo_sv <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double())
for (i in 1:(length(subjectindex)-1)) {
  newdata <- data.frame(subject = demo_data$subject[subjectindex[i]],
                          auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i+1]-1)], demo_data$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = FALSE),
                          auc_sv_unsorted = (0.5 * (demo_data$sv[subjectindex[i]] + demo_data$sv[subjectindex[i]+1]) +
                                               0.5 * (demo_data$sv[subjectindex[i]+1] + demo_data$sv[subjectindex[i]+2]) +
                                               0.5 * (demo_data$sv[subjectindex[i]+2] + demo_data$sv[subjectindex[i]+3])))
  demo_sv <- rbind(demo_sv, newdata)
}
```

>>>>

require(gtools)
demo_data = data.frame(level = rep(1:4,24))
sv = permutations(n = 4, r = 4, v = c(0.1,0.4,0.85,1))
m = 1
for (n in 1:(nrow(demo_data)/4)) {
  demo_data$subject[m:(m+3)] = rep(n,4)
  demo_data$sv[m:(m+3)] = sv[n,]
  m = m + 4
}
subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
demo_sv <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double())
for (i in 1:(length(subjectindex)-1)) {
  sv_sorted <- sort(demo_data$sv[subjectindex[i]:(subjectindex[i]+3)])
  newdata <- data.frame(subject = demo_data$subject[subjectindex[i]],
                        auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                   method = "trapezoid"),
                        auc_sv_unsorted = (0.5 * (demo_data$sv[subjectindex[i]] + demo_data$sv[subjectindex[i]+1]) +
                                               0.5 * (demo_data$sv[subjectindex[i]+1] + demo_data$sv[subjectindex[i]+2]) +
                                               0.5 * (demo_data$sv[subjectindex[i]+2] + demo_data$sv[subjectindex[i]+3])),
                        auc_sv_sorted = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
                                           0.5 * (sv_sorted[2] + sv_sorted[3]) +
                                           0.5 * (sv_sorted[3] + sv_sorted[4])))
  demo_sv <- rbind(demo_sv, newdata)
}
ggplot(demo_data, aes(x=level, y=sv, group=subject)) +
  geom_line(aes(color=subject), size = 1)

ggplot(demo_data[c((1*4+1):(1*4+4),(4*4+1):(4*4+4),(15*4+1):(15*4+4),(17*4+1):(17*4+4)),], aes(x=level, y=sv, group=subject)) +
  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0.03, h = 0.03))
ggplot(demo_data[c((3*4+1):(3*4+4),(5*4+1):(5*4+4),(9*4+1):(9*4+4),(11*4+1):(11*4+4)),], aes(x=level, y=sv, group=subject)) +
  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0.03, h = 0.03))
ggplot(demo_data[c((0*4+1):(0*4+4),(2*4+1):(2*4+4),(21*4+1):(21*4+4),(23*4+1):(23*4+4)),], aes(x=level, y=sv, group=subject)) +
  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0, h = 0.03))
```
